---
title: "Running Simulations with dexR"
author: "Sascha Holzhauer"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_vignette:
    number_sections: true
    toc: true
    toc_depth: 3
vignette: >
  %\VignetteIndexEntry{Running Simulations with dexR}
  %\VignetteEngine{knitr::rmarkdown}
  %\usepackage[utf8]{inputenc}
---


# Running

## Run locally

To run experiments with DEX locally, there are a few prerequesits which are decribed in the [DEX main documentation](https://gyges.iee.fraunhofer.de/doc/market.html#installation-and-configuration).

All procedures to acutally run a simulation are included in `hl_experiment`:

```{r, eval=FALSE}
source("/home/USER/dexr/scripts/dexpa-machine_machine.R")
dexpa$sim$version <- "testversion"	
dexpa$sim$id 	  <- "Testrun01"
source("/home/USER/dexr/scripts/dexpa-pversion_pversion.R")

dexR::hl_experiment(dexpa, basetime = as.numeric(round(strptime("30/09/19 12:00", "%d/%m/%y %H:%M"),"mins"))*1000)
```

## Run remotely

```{r, eval=FALSE}
source("/home/USER/dexr/scripts/dexpa-machine_machine.R")
dexpa$sim$version <- "testversion"	
dexpa$sim$id 	  <- "Testrun01"
source("/home/USER/dexr/scripts/dexpa-pversion_pversion.R")

dexR::hl_experiment_cluster(dexpa, basetime = as.numeric(round(strptime("30/09/19 12:00", "%d/%m/%y %H:%M"),"mins"))*1000),
		offset = round(basetime - as.numeric(Sys.time())*1000))
```


## Running step by step

In order to debug it may sometimes be helpful to execute the running process step by step. The following example is also given in ``.

```{r, eval=FALSE}
source("<path to git repository>/enavi/market/enavi-r/config/dexpa-machine_T460s.R")
dexpa$sim$version 	<- "testversion"	
dexpa$sim$id 		<- "Testrun01"

setwd(paste(dexpa$dirs$scripts, sep="/"))
source(paste(dexpa$dirs$scripts, dexpa$sim$version, "dexpa.R", sep="/"))

####### Configuration

dexpa$sim$timefactor	<- 60
dexpa$sim$duration	<- 10*60*60 # seconds

outputfile=paste(dexpa$dirs$output$logs, "/", dexpa$sim$id, "/", dexpa$sim$id, ".log", sep="")
outfilemarket = paste(dexpa$dirs$output$logs, "/", dexpa$sim$id, "/", dexpa$sim$id, "_market.log", sep="")
outfileemg = paste(dexpa$dirs$output$logs, "/", dexpa$sim$id, "/", dexpa$sim$id, "_emg.log", sep="")
outfileemg = paste(dexpa$dirs$output$logs, "/", dexpa$sim$id, "/", dexpa$sim$id, "_emg.log", sep="")

basetime = as.numeric(round(strptime("30/09/30 12:00", "%d/%m/%y %H:%M"),"mins"))*1000
offset = basetime - round(as.numeric(Sys.time())*1000)

shbasic::sh.ensurePath(outputfile, stripFilename = T)
con <- file(outputfile)
sink(con, append=TRUE)
sink(con, append=TRUE, type="message")

infoData <- data.frame()


####### Run experiment

futile.logger::flog.info("Starting backend with basetime = %s...", 
		format(as.POSIXct(basetime, tz="GTM", origin = "1970-01-01"), "%d/%m/%y %H:%M:%S"),,
		name = "dexr.hl.experiment.emg")
infoData <- dexR::hl_experiment_runbackend(dexpa, outfilesys = outfilemarket, 
		basetime = basetime, 
		offset = offset, 
		startServer=F)


dexR::hl_experiment_configemg(dexpa, outfilesys= if (is.null(dexpa$emg$emgconfigoutput)) "" else 
	paste(dexpa$dirs$output$logs, "/", dexpa$sim$id, "/", dexpa$sim$id, "_", dexpa$emg$emgconfigoutput, ".log", sep=""))


dexR::hl_experiment_awaitemgstartup(dexpa)


message = dexR::server_start(dexpa)
futile.logger::flog.info(message, name = "dexr.hl.experiment")	


futile.logger::flog.info("Wait for simulation to complete (Duration: %d / factor: %d = %d", dexpa$sim$duration, 
		dexpa$sim$timefactor, dexpa$sim$duration/dexpa$sim$timefactor, name = "dexr.hl.experiment")
Sys.sleep(dexpa$sim$duration/dexpa$sim$timefactor)


######## Stop services:

dexR::hl_experiment_stopemg(dexpa)

dexR::input_db_db2dump(dexpa, dumpdir = paste("dump_", dexpa$sim$id, sep=""))

try(dexR::createFullReport(dexpa, outputfile = paste("StageA_FullReport_", dexpa$sim$id, ".pdf", sep="")))

dexR::server_shutdown(dexpa)

if (outputfile != "") {
	sink()
	sink()
	sink(type="message")
}

lapply(DBI::dbListConnections(DBI::dbDriver("PostgreSQL")), DBI::dbDisconnect)
```
