---
title: "Analysing Simulations with dexR"
author: "Sascha Holzhauer"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_vignette:
    number_sections: true
    toc: true
    toc_depth: 3
    fig_width: 7
    fig_height: 4
    css:
      - !expr system.file("rmarkdown/templates/html_vignette/resources/vignette.css", package = "rmarkdown")
      - css/vignettes.css
vignette: >
  %\VignetteIndexEntry{Analysing Simulations with dexR}
  %\VignetteEngine{knitr::rmarkdown}
  %\usepackage[utf8]{inputenc}
---

# Figures

## Prerequesists

In order to run these examples, a working PostgreSQL-database is required with the following configuration in file `config/R/dexpa-figures.R`:

```{r, eval=FALSE, results="hide", echo=TRUE, messages=FALSE, warning=FALSE}
dexpa$db$host			<- "localhost"
dexpa$db$port			<- "5432"
dexpa$db$dbname			<- "enavi"
dexpa$db$username		<- "enavi"
dexpa$db$password		<- "enavi!"
dexpa$db$suname			<- "postgres"
dexpa$db$supassword		<- "WiScAn07"
```


## Comparisons: Clearing

### Clearing price per clearing by clearing time and by product

```{r, eval=TRUE, results="hide", echo=TRUE, messages=FALSE, warning=FALSE}
dexpas <- dexR::demo_prepare_db4figures()
dexR::hl_figure_clearing_comp_clearingPriceByCTbyProduct(dexpas, filename=NULL)
dexR::input_db_dropdbs(dexpas)
```

### Number of considered requests per clearing by clearing time

```{r, eval=TRUE, results="hide", echo=TRUE, messages=FALSE, warning=FALSE}
dexpas <- dexR::demo_prepare_db4figures()
dexR::hl_figure_clearing_comp_numConsideredRequests(dexpas, filename=NULL)
dexR::input_db_dropdbs(dexpas)
```

## Comparisons: Requests

### Nnumber of received requests per status by delivery start time

```{r, eval=TRUE, results="hide", echo=TRUE, messages=FALSE, warning=FALSE}
dexpas <- dexR::demo_prepare_db4figures()
dexR::hl_figure_requests_numRequests_comp_byStatusByStartT(dexpas, filename=NULL)
dexR::input_db_dropdbs(dexpas)
```

# Comparing Runs/Scenarios

The generic way of comparing data of several simulation runs, i.e. combining the data to visualise in one plot, is the following:

1. For each data set to compare
	+ Store dumpfile into database
	+ Generate a `dexpa`-list for each run and store them in a list `dexpas`.
2. Pass the list `dexpas` to a comparison function

However, there a few high level functions that take a list of `dexpa` configurations and do not require the storage of combined data:

* hl_comp_aggregate_aftcompositions
* hl_comp_cell_aftcomposition# Comparing Runs/Scenarios
