---
title: "DEX Single Run Report"
header-includes:
  - \widowpenalties 1 150
    \useoutertheme[footline=authortitle, subsection=false]{miniframes}
author: '`r dexpa$reports$author`'
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
    beamer_presentation:
        keep_tex: false
        colortheme: orchid
        df_print: kable
        fig_width: 7
        fig_height: 4
        fig_caption: true
        incremental: false
        slide_level: 3
        theme: Singapore
        fonttheme: "structurebold"
        toc: true
        template: DEX_tmpl_comparison_slides.tex
fontsize: 8pt
---

```{r, eval=TRUE, include = FALSE}
setwd(paste(dexpa$dirs$scripts, sep="/"))
dexpa$fig$init <- function(simp, outdir, filename) {}
dexpa$fig$close<- function() {}
```
# Parameters
## General Information
### General Information
* IDs:
```{r, eval=TRUE, results="asis", message=FALSE, error=FALSE, warning=FALSE, echo=FALSE}
invisible(futile.logger::flog.threshold(futile.logger::ERROR, name='dexr'))
input_db_runID(dexpa)
cat('\n')
invisible(futile.logger::flog.threshold(futile.logger::INFO, name='dexr'))
```
* Date: `r format(Sys.time(), "%a %b %d %H:%M:%S %Y")`

## Product Information
### Product Information {.allowframebreaks}
```{r, eval=TRUE, results="asis", message=FALSE, error=FALSE, warning=FALSE, echo=FALSE}
invisible(futile.logger::flog.threshold(futile.logger::ERROR, name='dexr'))
cat("#### Product Information") 
print(dexR::output_table_param_products(dexpa))
invisible(futile.logger::flog.threshold(futile.logger::INFO, name='dexr'))
```

## Market Information
### Market Information {.allowframebreaks}
```{r, eval=TRUE, results="asis", message=FALSE, error=FALSE, warning=FALSE, echo=FALSE}
invisible(futile.logger::flog.threshold(futile.logger::ERROR, name='dexr'))
cat("#### Market Information")
print(dexR::output_table_param_marketinfo(dexpa))
invisible(futile.logger::flog.threshold(futile.logger::INFO, name='dexr'))
```

## Client Information
```{r, eval=TRUE, results="asis", message=FALSE, warning=FALSE, echo=FALSE}
invisible(futile.logger::flog.threshold(futile.logger::ERROR, name='dexr'))
cat("\n### Client Information") 
dexR::output_table_param_clients(dexpa)
invisible(futile.logger::flog.threshold(futile.logger::INFO, name='dexr'))
```

# Time Series: Clearing
## Clearing: Number of considered requests
### Clearing: Number of considered requests
```{r, eval=TRUE, results="hide", echo=FALSE, messages=FALSE, warning=FALSE}
dexR::hl_figure_clearing_numConsideredRequests(dexpa)
```

## Clearing: Price Statistics
### Clearing: Price Statistics
```{r, eval=TRUE, results="hide", echo=FALSE, messages=FALSE, warning=FALSE}
dexpa$fig$height <- 750
dexR::hl_figure_clearing_clearingPriceByCTbyProduct(dexpa)
```

# Time Series: Energy
## Requested Energy by Status (Residual)
### Requested Energy by Status (Residual)
```{r, eval=TRUE, results="hide", echo=FALSE, messages=FALSE, warning=FALSE}
dexpa$fig$height <- 750
dexR::hl_figure_energy_requested_byStatusByStartT(dexpa, type="residual", skiplegend=T)
```

## Requested Energy by Status (Load)
### Requested Energy by Status (Load)
```{r, eval=TRUE, results="hide", echo=FALSE, messages=FALSE, warning=FALSE}
dexpa$fig$height <- 750
dexR::hl_figure_energy_requested_byStatusByStartT(dexpa, type="load", skiplegend=T)
```

## Requested Energy by Status (Generation)
### Requested Energy by Status (Generation)
```{r, eval=TRUE, results="hide", echo=FALSE, messages=FALSE, warning=FALSE}
dexpa$fig$height <- 750
dexR::hl_figure_energy_requested_byStatusByStartT(dexpa, type="generation", skiplegend=T)
```

## Requested Energy summed
### Requested Energy summed
```{r, eval=TRUE, results="hide", echo=FALSE, messages=FALSE, warning=FALSE}
dexpa$fig$height <- 750
dexR::hl_figure_energy_requested_sumByStartT(dexpa)
```

## Requested Energy (Generation, Load, Residual)
### Requested Energy (Generation, Load, Residual)
```{r, eval=TRUE, results="hide", echo=FALSE, messages=FALSE, warning=FALSE}
dexpa$fig$height <- 750
dexR::hl_figure_energy_requested_sumLoadGenByStartT(dexpa)
```

## Aggregated Energy Figures
### Aggregated Energy Figures
```{r, eval=TRUE, results="asis", echo=FALSE, messages=FALSE, warning=FALSE}
invisible(futile.logger::flog.threshold(futile.logger::ERROR, name='dexr'))
dexR::hl_statistics_energy(dexpa)
invisible(futile.logger::flog.threshold(futile.logger::INFO, name='dexr'))
```

# Time Series: Requests
## Request Statistics by status and submission time
### Request Statistics by status and submission time
```{r, eval=TRUE, results="hide", echo=FALSE, messages=FALSE, warning=FALSE}
dexpa$fig$height <- 950
dexR::hl_figure_requests_numRequests_byStatusBySubmT(dexpa)
```

### Request Statistics by status and delivery start time
```{r, eval=TRUE, results="hide", echo=FALSE, messages=FALSE, warning=FALSE}
dexpa$fig$height <- 950
dexR::hl_figure_requests_numRequests_byStatusByStartT(dexpa)
```

### Request Statistics by requests type and delivery start time
```{r numReqByTypeByStart, eval=TRUE, results="hide", echo=FALSE, messages=FALSE, warning=FALSE}
dexpa$fig$height <- 950
hl_figure_requests_numRequests_byTypeByStartT(dexpa)
```

## Request Statistics by product and submission time
### Request Statistics by product and submission time
```{r, eval=TRUE, results="hide", echo=FALSE, messages=FALSE, warning=FALSE}
dexpa$fig$height <- 750
dexR::hl_figure_requests_numRequests_byProductBySubmT(dexpa)
```

## Request Statistics by product and delivery start time
### Request Statistics by product and delivery start time
```{r, eval=TRUE, results="hide", echo=FALSE, messages=FALSE, warning=FALSE}
dexpa$fig$height <- 750
dexR::hl_figure_requests_numRequests_byProductByStartT(dexpa)
```
