---
title: "DEX Comparison Report"
header-includes:
  - \widowpenalties 1 150
author: '`r dexpa$reports$author`'
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
    beamer_presentation:
        keep_tex: false
        colortheme: orchid
        df_print: kable
        fig_width: 7
        fig_height: 4
        fig_caption: true
        incremental: false
        slide_level: 3
        theme: Singapore
        fonttheme: "structurebold"
        toc: true
        template: DEX_tmpl_comparison_slides.tex
fontsize: 8pt
---

```{r, eval=TRUE, include = FALSE}
setwd(paste(dexpas[[1]]$dirs$scripts, sep="/"))
dexpas <- lapply(dexpas, function(dp) {
	dp$fig$init <- function(simp, outdir, filename) {}
	dp$fig$close<- function() {}
	dp$fig$skiptitles <- T
	dp
})
```
# Parameters
## General Information
### General Information
* IDs:
```{r, eval=TRUE, results="asis", message=FALSE, error=FALSE, warning=FALSE, echo=FALSE}
invisible(futile.logger::flog.threshold(futile.logger::ERROR, name='dexr'))
for (dp in dexpas) {
	cat('\n')
	cat("  + ", input_db_runID(dp), sep = "")
}
cat('\n')
invisible(futile.logger::flog.threshold(futile.logger::INFO, name='dexr'))
```
* Date: `r format(Sys.time(), "%a %b %d %H:%M:%S %Y")`

## Product Information
### Product Information {.allowframebreaks}
```{r, eval=TRUE, results="asis", message=FALSE, error=FALSE, warning=FALSE, echo=FALSE}
invisible(futile.logger::flog.threshold(futile.logger::ERROR, name='dexr'))
if (dexR::param_marketproductsdiffer(dexpas)) {
  for (dp in dexpas) {
  	cat('\n')
  	cat("#### Market Information (", input_db_runID(dp), ")", sep = "")
  	print(dexR::output_table_param_products(dp))
  }
} else {
  cat("#### Market Information")
  print(dexR::output_table_param_products(dexpas[[1]]))
}
invisible(futile.logger::flog.threshold(futile.logger::INFO, name='dexr'))
```

## Market Information
### Market Information {.allowframebreaks}
```{r, eval=TRUE, results="asis", message=FALSE, error=FALSE, warning=FALSE, echo=FALSE}
invisible(futile.logger::flog.threshold(futile.logger::ERROR, name='dexr'))
for (dp in dexpas) {
  	cat('\n')
  	cat("#### Market Information (", input_db_runID(dp), ")", sep = "")
  	print(dexR::output_table_param_marketinfo(dp))
}
invisible(futile.logger::flog.threshold(futile.logger::INFO, name='dexr'))
```

## Client Information
```{r, eval=TRUE, results="asis", message=FALSE, warning=FALSE, echo=FALSE}
invisible(futile.logger::flog.threshold(futile.logger::ERROR, name='dexr'))
if (dexR::param_clientsdiffer(dexpas)) {
  for (dp in dexpas) {
  	cat("\n### Client Information (", input_db_runID(dp), ")", sep = "") 
  	dexR::output_table_param_clients(dp)
  }
} else {
  cat("\n### Client Information") 
  	dexR::output_table_param_clients(dexpas[[1]])
}
invisible(futile.logger::flog.threshold(futile.logger::INFO, name='dexr'))
```

# Time Series: Clearing

## Clearing: Number of Considered Requests by Delivery
### Clearing: Number of Considered Requests by Delivery
```{r, eval=TRUE, results="hide", echo=FALSE, messages=FALSE, warning=FALSE}
dexR::hl_figure_clearing_comp_numConsideredRequests(dexpas)
```

## Clearing: Prices by Delivery
### Clearing: Prices by Delivery
```{r, eval=TRUE, results="hide", echo=FALSE, messages=FALSE, warning=FALSE}
dexpas[[1]]$fig$height <- 750
dexR::hl_figure_clearing_comp_clearingPriceByCTbyProduct(dexpas)
```


```{r, eval=TRUE, results="hide", echo=FALSE, messages=FALSE, warning=FALSE}
if (dexpa$fig$show$costs$summed_delivery) {
  cat("\n## Summed Costs by Delivery")
  cat("\n### Summed Costs by Delivery")
  dexpas[[1]]$fig$height <- 750
  dexR::hl_figure_energycosts_requested_comp_sumByStartT(dexpas, skiplegend=T)
}
```

```{r, eval=TRUE, results="hide", echo=FALSE, messages=FALSE, warning=FALSE}
if (dexpa$fig$show$costs$costgini_gen_delivery) {
  cat("\n## Energy, Costs, and Gini Coefficient for Generation by Delivery")
  cat("\n### Energy, Costs, and Gini Coefficient for Generation by Delivery")
  dexpas[[1]]$fig$height <- 750
  dexR::hl_figure_energycosts_requests_comp_giniByStartT(dexpas, type = "gen", skiplegend=T)
}
```

```{r, eval=TRUE, results="hide", echo=FALSE, messages=FALSE, warning=FALSE}
if (dexpa$fig$show$costs$costgini_load_delivery) {
  cat("\n## Energy, Costs, and Gini Coefficient for Loads by Delivery")
  cat("\n### Energy, Costs, and Gini Coefficient for Loads by Delivery")
  dexpas[[1]]$fig$height <- 750
  dexR::hl_figure_energycosts_requests_comp_giniByStartT(dexpas, type = "load", skiplegend=T)
}
```

# Time Series: Energy

## Requested Energy (Generation, Load, Residual) by Delivery
### Requested Energy (Generation, Load, Residual) by Delivery
```{r energy_req_type, eval=TRUE, echo=FALSE, warning=FALSE, messages=FALSE, results="hide"}
dexpas[[1]]$fig$height <- 750
dexR::hl_figure_energy_requested_comp_sumLoadGenByStartT(dexpas)
```

## Requested Energy by type and delivery
### Requested Energy by type and delivery
```{r, eval=TRUE, results="hide", echo=FALSE, messages=FALSE, warning=FALSE}
dexpas[[1]]$fig$height <- 750
dexR::hl_figure_energy_requested_comp_sumGenByTypeStartT(dexpas, skiplegend=T)
```

```{r, eval=TRUE, results="hide", echo=FALSE, messages=FALSE, warning=FALSE}
if (dexpa$fig$show$energy$summed_delivery) {
  cat("\n## Requested Energy summed by delivery")
  cat("\n### Requested Energy summed by delivery")
  dexpas[[1]]$fig$height <- 750
  dexR::hl_figure_energy_requested_comp_sumByStartT(dexpas)
}
```

## Requested Energy (Generation) by Status and Delivery
### Requested Energy (Generation) by Status and Delivery
```{r, eval=TRUE, results="hide", echo=FALSE, messages=FALSE, warning=FALSE}
dexpas[[1]]$fig$height <- 750
dexR::hl_figure_energy_requested_comp_byStatusByStartT(dexpas, type="generation", skiplegend=T)
```

## Requested Energy
### Requested Energy (Load) by Status and Delivery
```{r, eval=TRUE, results="hide", echo=FALSE, messages=FALSE, warning=FALSE}
dexpas[[1]]$fig$height <- 750
dexR::hl_figure_energy_requested_comp_byStatusByStartT(dexpas, type="load", skiplegend=T)
```


```{r, eval=TRUE, results="hide", echo=FALSE, messages=FALSE, warning=FALSE}
if (dexpa$fig$show$energy$residual_status_delivery) {
  cat("\n## Requested Energy (Residual) by Status and Delivery")
  cat("\n### Requested Energy (Residual) by Status and Delivery")
  dexpas[[1]]$fig$height <- 750
  dexR::hl_figure_energy_requested_comp_byStatusByStartT(dexpas, type="residual", skiplegend=T)
}
```

## Aggregated Energy Figures
### Aggregated Energy Figures
```{r, eval=TRUE, results="asis", echo=FALSE, messages=FALSE, warning=FALSE}
invisible(futile.logger::flog.threshold(futile.logger::ERROR, name='dexr'))
dexR::hl_statistics_comp_energy(dexpas)
invisible(futile.logger::flog.threshold(futile.logger::INFO, name='dexr'))
```

# Time Series: Requests
### Request Statistics by status and delivery
```{r, eval=TRUE, results="hide", echo=FALSE, messages=FALSE, warning=FALSE}
dexpas[[1]]$fig$height <- 950
dexR::hl_figure_requests_numRequests_comp_byStatusByStartT(dexpas, skiplegend=T)
```

### Request Statistics by requests type and delivery
```{r numReqByTypeByStart, eval=TRUE, results="hide", echo=FALSE, messages=FALSE, warning=FALSE}
dexpas[[1]]$fig$height <- 950
hl_figure_requests_numRequests_comp_byTypeByStartT(dexpas, skiplegend=T)
```

```{r, eval=TRUE, results="hide", echo=FALSE, messages=FALSE, warning=FALSE}
if (dexpa$fig$show$requests$product_delivery) {
  cat("\n## Request Statistics by product and delivery")
  cat("\n### Request Statistics by product and delivery")
  dexpas[[1]]$fig$height <- 750
  dexR::hl_figure_requests_numRequests_comp_byProductByStartT(dexpas, skiplegend=T)
}
```

```{r, eval=TRUE, results="hide", echo=FALSE, messages=FALSE, warning=FALSE}
if (dexpa$fig$show$requests$status_submission) {
  cat("\n## Request Statistics by status and submission")
  cat("\n### Request Statistics by status and submission")
  dexpas[[1]]$fig$height <- 950
  dexR::hl_figure_requests_numRequests_comp_byStatusBySubmT(dexpas, skiplegend=T)
}
```

```{r, eval=TRUE, results="hide", echo=FALSE, messages=FALSE, warning=FALSE}
if (dexpa$fig$show$requests$product_submission) {
  cat("\n## Request Statistics by product and submission")
  cat("\n### Request Statistics by product and submission")
  dexpas[[1]]$fig$height <- 750
  dexR::hl_figure_requests_numRequests_comp_byProductBySubmT(dexpas, skiplegend=T)
}
```