---
title: "DEX Comparison Report"
header-includes:
  - \widowpenalties 1 150
author: '`r dexpa$reports$author`'
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
    beamer_presentation:
        keep_tex: false
        colortheme: orchid
        df_print: kable
        fig_width: 7
        fig_height: 4
        fig_caption: true
        incremental: false
        slide_level: 3
        theme: Singapore
        fonttheme: "structurebold"
        toc: true
        template: DEX_tmpl_comparison_slides.tex
fontsize: 8pt
---

```{r, eval=TRUE, include = FALSE}
setwd(paste(dexpas[[1]]$dirs$scripts, sep="/"))
dexpas <- lapply(dexpas, function(dp) {
	dp$fig$init <- function(simp, outdir, filename) {}
	dp$fig$close<- function() {}
	dp$fig$skiptitles <- T
	dp
})
```
# Parameters
## General Information
* IDs:
```{r param_general, eval=TRUE, results="asis", message=FALSE, error=FALSE, warning=FALSE, echo=FALSE}
invisible(futile.logger::flog.threshold(futile.logger::ERROR, name='dexr'))
for (dp in dexpas) {
	cat('\n')
	cat("  + ", input_db_runID(dp), sep = "")
}
cat('\n')
invisible(futile.logger::flog.threshold(futile.logger::INFO, name='dexr'))
```
* Date: `r format(Sys.time(), "%a %b %d %H:%M:%S %Y")`

## Product Information {.allowframebreaks}
```{r param_producs, eval=TRUE, results="asis", message=FALSE, error=FALSE, warning=FALSE, echo=FALSE}
invisible(futile.logger::flog.threshold(futile.logger::ERROR, name='dexr'))
if (dexR::param_marketproductsdiffer(dexpas)) {
  for (dp in dexpas) {
  	cat('\n')
  	cat("### Product Information (", input_db_runID(dp), ")", sep = "")
  	cat('\n')
  	print(dexR::output_table_param_products(list(dp), skipcolumns = c("id")))
  }
} else {
  cat("### Product Information")
  print(dexR::output_table_param_products(dexpas[1]), skipcolumns = c("id"))
}
invisible(futile.logger::flog.threshold(futile.logger::INFO, name='dexr'))
```

## Market Information 
### Market Information{.allowframebreaks}
```{r param_market, eval=TRUE, results="asis", message=FALSE, error=FALSE, warning=FALSE, echo=FALSE}
invisible(futile.logger::flog.threshold(futile.logger::ERROR, name='dexr'))
if (dexR::param_marketinfodiffer(dexpas)) {
  for (dp in dexpas) {
    	cat('\n')
    	cat("#### Market Information (", input_db_runID(dp), ")", sep = "")
    	cat('\n')
    	print(dexR::output_table_param_marketinfo(dp))
  }
} else {
    cat("\n#### Market Information\n")
    print(dexR::output_table_param_marketinfo(dexpas[[1]]))
}
invisible(futile.logger::flog.threshold(futile.logger::INFO, name='dexr'))
```

## Client Information
```{r param_client, eval=TRUE, results="asis", message=FALSE, error=FALSE, warning=FALSE, echo=FALSE}
invisible(futile.logger::flog.threshold(futile.logger::ERROR, name='dexr'))
if (dexR::param_clientsdiffer_runs(dexpas)) {
  for (dp in dexpas) {
  	cat("\n### Client Information (", input_db_runID(dp), "){.allowframebreaks}\n", sep = "") 
    dexR::output_table_param_clients(dp, linespertable = 16)
  }
} else {
  cat("\n### Client Information{.allowframebreaks}")
  cat('\n')
  dexR::output_table_param_clients(dexpas[[1]])
}
invisible(futile.logger::flog.threshold(futile.logger::INFO, name='dexr'))
```

# Time Series: Requests
## Request Statistics By delivery
### Request Statistics by status and delivery
```{r requests_num_statusStartT, eval=TRUE, results="hide", echo=FALSE, message=FALSE, warning=FALSE}
dexpas[[1]]$fig$height <- 950
dexR::hl_figure_requests_numRequests_comp_byStatusByStartT(dexpas, skiplegend=F)
```

### Request Statistics by requests type and delivery
```{r requests_num_typeStart, eval=TRUE, results="hide", echo=FALSE, message=FALSE, warning=FALSE}
dexpas[[1]]$fig$height <- 950
dexR::hl_figure_requests_numRequests_comp_byTypeByStartT(dexpas, skiplegend=T)
```

```{r requests_num_productStarT, eval=TRUE, results="asis", echo=FALSE, message=FALSE, warning=FALSE}
if (dexpa$fig$show$requests$product_delivery) {
  invisible(futile.logger::flog.threshold(futile.logger::ERROR, name='dexr'))
  cat('\n')
  cat("### Request Statistics by product and delivery")
  cat('\n')
  dexpas[[1]]$fig$height <- 750
  dexR::hl_figure_requests_numRequests_comp_byProductByStartT(dexpas, skiplegend=T)
  invisible(futile.logger::flog.threshold(futile.logger::INFO, name='dexr'))
}
```

```{r clients_StartT, eval=TRUE, results="asis", echo=FALSE, message=FALSE, warning=FALSE}
if (dexpa$fig$show$requests$clients_delivery) {
  invisible(futile.logger::flog.threshold(futile.logger::ERROR, name='dexr'))
  cat('\n')
  cat("### Request Statistics: Number of clients by delivery")
  cat('\n')
  dexpas[[1]]$fig$height <- 750
  dexR::hl_figure_requests_numClients_comp_ByStartT(dexpas, skiplegend=T)
  invisible(futile.logger::flog.threshold(futile.logger::INFO, name='dexr'))
}
```

```{r requests_num_submission, eval=TRUE, results="asis", echo=FALSE, message=FALSE, warning=FALSE}
if (dexpa$fig$show$requests$status_submission || dexpa$fig$show$requests$product_submission) {
  cat('\n')
  cat("## Request Statistics by submission")
  cat('\n')
}
```

```{r requests_num_statusSubmission, eval=TRUE, results="asis", echo=FALSE, message=FALSE, warning=FALSE}
if (dexpa$fig$show$requests$status_submission) {
  invisible(futile.logger::flog.threshold(futile.logger::ERROR, name='dexr'))
  cat('\n')
  cat("### Request Statistics by status and submission")
  dexpas[[1]]$fig$height <- 950
  dexR::hl_figure_requests_numRequests_comp_byStatusBySubmT(dexpas, skiplegend=T)
  invisible(futile.logger::flog.threshold(futile.logger::INFO, name='dexr'))
}
```

```{r requests_num_procudtSubmission, eval=TRUE, results="asis", echo=FALSE, message=FALSE, warning=FALSE}
if (dexpa$fig$show$requests$product_submission) {
  invisible(futile.logger::flog.threshold(futile.logger::ERROR, name='dexr'))
  cat('\n')
  cat("### Request Statistics by product and submission")
  cat('\n')
  dexpas[[1]]$fig$height <- 750
  dexR::hl_figure_requests_numRequests_comp_byProductBySubmT(dexpas, skiplegend=T)
  invisible(futile.logger::flog.threshold(futile.logger::INFO, name='dexr'))
}
```
# Time Series: Energy

## Requested Energy by Delivery
### Requested Energy (Generation, Load, Residual) by Delivery
```{r energy_req_type, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE, results="hide"}
dexpas[[1]]$fig$height <- 750
dexR::hl_figure_energy_requested_comp_sumLoadGenByStartT(dexpas)
```

### Requested Energy by type and delivery
```{r energy_req_typeStartT, eval=TRUE, results="hide", echo=FALSE, message=FALSE, warning=FALSE}
dexpas[[1]]$fig$height <- 750
dexR::hl_figure_energy_requested_comp_sumGenByTypeStartT(dexpas, skiplegend=T)
```

```{r energy_reqSum_startT, eval=TRUE, results="asis", echo=FALSE, messages=FALSE, warning=FALSE}
if (dexpa$fig$show$energy$summed_delivery) {
  invisible(futile.logger::flog.threshold(futile.logger::ERROR, name='dexr'))
  cat('\n')
  cat("### Requested Energy summed by delivery\n")
  dexpas[[1]]$fig$height <- 750
  dexR::hl_figure_energy_requested_comp_sumByStartT(dexpas)
  invisible(futile.logger::flog.threshold(futile.logger::INFO, name='dexr'))
}
```

### Requested Energy (Generation) by Status and Delivery
```{r energy_gen_statusStartT, eval=TRUE, results="hide", echo=FALSE, message=FALSE, warning=FALSE}
dexpas[[1]]$fig$height <- 750
dexR::hl_figure_energy_requested_comp_byStatusByStartT(dexpas, type="generation", skiplegend=T)
```

### Requested Energy (Load) by Status and Delivery
```{r energy_load_statusStartT, eval=TRUE, results="hide", echo=FALSE, message=FALSE, warning=FALSE}
dexpas[[1]]$fig$height <- 750
dexR::hl_figure_energy_requested_comp_byStatusByStartT(dexpas, type="load", skiplegend=T)
```


```{r energy_res_statusStartT, eval=TRUE, results="asis", echo=FALSE, message=FALSE, warning=FALSE}
if (dexpa$fig$show$energy$residual_status_delivery) {
  invisible(futile.logger::flog.threshold(futile.logger::ERROR, name='dexr'))
  cat('\n')
  cat("### Requested Energy (Residual) by Status and Delivery")
  cat('\n')
  dexpas[[1]]$fig$height <- 750
  dexR::hl_figure_energy_requested_comp_byStatusByStartT(dexpas, type="residual", skiplegend=T)
  invisible(futile.logger::flog.threshold(futile.logger::INFO, name='dexr'))
}
```

## Aggregated Energy Figures
### Aggregated Energy Figures
```{r energy_table, eval=TRUE, results="asis", echo=FALSE, messages=FALSE, warning=FALSE}
invisible(futile.logger::flog.threshold(futile.logger::ERROR, name='dexr'))
dexR::hl_statistics_comp_energy(dexpas)
invisible(futile.logger::flog.threshold(futile.logger::INFO, name='dexr'))
```
# Time Series: Clearing

## Clearing: Number of Considered Requests
### Clearing: Number of Considered Requests by Delivery
```{r clearing_numReq_startT, eval=TRUE, results="hide", echo=FALSE, messages=FALSE, warning=FALSE}
dexR::hl_figure_clearing_comp_numConsideredRequests(dexpas)
```

## Clearing: Requested Prices
### Clearing: Average Requested Prices by Type and Delivery
```{r clearing_priceRey_typeStartT, eval=TRUE, results="asis", echo=FALSE, message=FALSE, warning=FALSE}
invisible(futile.logger::flog.threshold(futile.logger::ERROR, name='dexr'))
if (dexpa$fig$show$prices$avg_delivery) {
dexR::hl_figure_prices_requested_comp_byTypeStartT(dexpas, skiplegend=T)
invisible(futile.logger::flog.threshold(futile.logger::INFO, name='dexr'))
}
```

## Clearing: Prices
### Clearing: Prices by Delivery
```{r clearing_price_startT, eval=TRUE, results="hide", echo=FALSE, messages=FALSE, warning=FALSE}
dexpas[[1]]$fig$height <- 750
dexR::hl_figure_clearing_comp_clearingPriceByCTbyProduct(dexpas)
```

```{r clearing_gini_header, eval=TRUE, results="asis", echo=FALSE, messages=FALSE, warning=FALSE}
if (dexpa$fig$show$costs$summed_delivery || dexpa$fig$show$costs$costgini_gen_delivery || dexpa$fig$show$costs$costgini_load_delivery) {
  cat('\n')
  cat("## Summed Costs\n")
}
```

```{r clearing_costs_startT, eval=TRUE, results="asis", echo=FALSE, message=FALSE, warning=FALSE}
invisible(futile.logger::flog.threshold(futile.logger::ERROR, name='dexr'))
if (dexpa$fig$show$costs$summed_delivery) {
  cat('\n')
  cat("### Summed Costs by Delivery\n")
  dexpas[[1]]$fig$height <- 750
  dexR::hl_figure_energycosts_requested_comp_sumByStartT(dexpas, skiplegend=T)
}
invisible(futile.logger::flog.threshold(futile.logger::INFO, name='dexr'))
```

```{r clearing_giniGen_startT, eval=TRUE, results="asis", echo=FALSE, message=FALSE, warning=FALSE}
if (dexpa$fig$show$costs$costgini_gen_delivery) {
  invisible(futile.logger::flog.threshold(futile.logger::ERROR, name='dexr'))
  cat('\n')
  cat("### Energy, Costs, and Gini Coefficient for Generation by Delivery\n")
  cat('\n')
  dexpas[[1]]$fig$height <- 750
  dexR::hl_figure_energycosts_requests_comp_giniByStartT(dexpas, type = "gen", skiplegend=T)
  invisible(futile.logger::flog.threshold(futile.logger::INFO, name='dexr'))
}
```

```{r clearing_giniLoad_startT, eval=TRUE, results="asis", echo=FALSE, message=FALSE, warning=FALSE}
invisible(futile.logger::flog.threshold(futile.logger::ERROR, name='dexr'))
if (dexpa$fig$show$costs$costgini_load_delivery) {
  cat('\n')
  cat("### Energy, Costs, and Gini Coefficient for Loads by Delivery\n")
  dexpas[[1]]$fig$height <- 750
  dexR::hl_figure_energycosts_requests_comp_giniByStartT(dexpas, type = "load", skiplegend=T)
}
invisible(futile.logger::flog.threshold(futile.logger::INFO, name='dexr'))
```

```{r gini_table, eval=TRUE, results="asis", echo=FALSE, messages=FALSE, warning=FALSE}
invisible(futile.logger::flog.threshold(futile.logger::ERROR, name='dexr'))
if (dexpa$fig$show$costs$costgini_aggregate) {
  cat("### Aggregated Gini Figures\n")
  dexR::hl_statistics_comp_gini(dexpas)
}
invisible(futile.logger::flog.threshold(futile.logger::INFO, name='dexr'))
```